Parsing Tweets into Universal Dependencies

### 2017-11-30 paper.tex
fix equ.
revise p1 - p3

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}

@@

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, both because domain
adaptation is required, but also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have  good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreement among our annotations and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
baseline parser can be achieved with our distillation method and that it outperforms
other state-of-the-art parsers in both accuracy and running speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
We also characterize the difficulties of creating such annotation.

\item We introduce and evaluate a system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  Experimental results show
it performs better than a stack of the state-of-the-art alternatives.
\nascomment{say it
  performs better than existing systems?}\yjcomment{added.}

@@

We release our dataset and our system as open-source software at
\url{http://anonymized}.

@@

We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest Twitter dependencies annotation
(\S\ref{sec:tweebank}).
Then we introduce the differences in our tokenization
(\S\ref{sec:tok-anno}) and part-of-speech (\S\ref{sec:pos-anno}) (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011}, respectively, on which {\sc Tweebank v1} was built. 
We describe our effort of adapting the
UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
Finally, we present our process of creating a new tweet treebank, {\sc
  Tweebank v2}, and characterize
the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).

@@

The annotation effort we describe stands in contrast to previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added dependencies to a portion of the data
annotated with POS tags by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT} after rule-based tokenization \citep{ICWSM101540}.
Kong et al.~also contributed a system for parsing;
we defer the discussion of their parser to \S\ref{sec:parsing}.

Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by nonnative speakers, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic.''
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

\subsection{Tokenization}\label{sec:tok-anno}
Our tokenization strategy lies between the strategy of
\citet{ICWSM101540} and that of UD.
There is a significant tradeoff  between preservation of original tweet content and respecting
the UD guidelines.

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as token.
They therefore more aggressively split
clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
is tokenized as {\it it} and {\it s} when {\it s} is a copula). But acronyms is not touched
in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
and left acronyms like {\em idc} as a single token.
\yicomment{does UD support normalization for
  acronyms? Did not see it from website, need to check. related to
  ``idc''} \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}
\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
normalization was just annotated for data study.}

In the different direction of splitting tokens, UD guidelines also suggest to merge
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain mult-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Before turning to UD annotations, we (re)annotated the data with 
POS, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases, conflicts arose between the UD English 
treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

Compared to the coarse-grained POS tagging effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference follows from the difference in
tokenization.  As discussed above, UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}.  In particular, Gimpel et al.~opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}.  
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check} \yjcomment{checked}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
{\arg\,\min}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
  \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a stack of the state-of-the-art systems (named as the {\it SOTA stack}):
Stanford CoreNLP tokenizer,
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
Our system differs with the SOTA stack in the tokenization and parser components.
From Table \ref{tbl:pipline}, our system outperforms the SOTA stack when
evaluated in pipeline manner.
The results also emphasize the
importance of segmentation:  without gold segmentation, UD parsing
performance drops by more than four points.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}

@@

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing? (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages \yicomment{texts?} is challenging, both \yicomment{not only} because domain
adaptation is required, but also because \yicomment{delete `because' ?} creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose \yicomment{believe?} that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) \yicomment{no need for parenthesis} universal dependencies.
We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s). check abstract, same sentence, different singularity/plurality. I think should be `disagreement' and `annotations'} and find that
consistent annotation \yicomment{again, it needs to be the same all the time at least for me.} is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM)\yicomment{need cite lstm/bi-lstm here?} tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT} \yicomment{no need for parenthesis?}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
baseline parser can be achieved with our distillation method and that \yicomment{delete `that'?} it outperforms
other state-of-the-art parsers in both accuracy and running speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech \yicomment{POS} tagging, and labeled universal dependencies annotation.
We also characterize the difficulties of creating such annotation.

\item We introduce and evaluate a \yicomment{pipeline} system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  Experimental results show
it performs better than a stack of the state-of-the-art alternatives.
\nascomment{say it
  performs better than existing systems?}\yjcomment{added.}

@@

We release our dataset and our \yicomment{delete `our'} system as open-source software \yicomment{delete `as open-source software'?} at
\url{http://anonymized}.

@@

We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is \yicomment{was} the largest \yicomment{unlabelled} Twitter dependencies annotation
(\S\ref{sec:tweebank}).
Then we introduce the differences in our tokenization
(\S\ref{sec:tok-anno}) and part-of-speech (\S\ref{sec:pos-anno}) (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011}, respectively, on which {\sc Tweebank v1} was built. 
We describe our effort of adapting the
UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
Finally, we present our process of creating a new tweet treebank, {\sc
  Tweebank v2}, and characterize
the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).

@@

The annotation effort we describe stands in contrast to \yicomment{the?} previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added \yicomment{unlabelled} dependencies to a portion of the data
annotated with POS tags by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT} after rule-based tokenization \citep{ICWSM101540}.
Kong et al.~also contributed a system for parsing;
we defer the discussion of their parser to \S\ref{sec:parsing}.

Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by nonnative speakers \yicomment{should not emphasize non-native speakers (v2 also built by non-native speakers), but emphasize annotators with only cursory training, no clear annotation guidelines, no consensus/agreement on controversial cases, allow annotators to underspecify part of the tree and allow multiple different trees for the same tweets}, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic''\yicomment{(e.g. retweet sign, topical hashtags, ...)}.
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

\subsection{Tokenization}\label{sec:tok-anno}
Our tokenization strategy lies between the strategy of
\citet{ICWSM101540} and that of UD.
There is a significant \yicomment{significant? not really} tradeoff between preservation of original tweet content and respecting
the UD guidelines.

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as a token.
They therefore more aggressively split
clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{I think the examples are not contractions (can't), is there a name for such words?}. But acronyms are not touched
in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
and left acronyms like {\em idc} as a single token. \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}
\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
normalization was just annotated for data study.}

In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain mult-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Before turning to UD \yicomment{dependencies} annotations, we (re)annotated the data with 
POS \yicomment{tags}, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases, conflicts arose between the UD English 
treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  \yicomment{The conflicts should refer to a {\bf noncorresponding tag} from that of gimpel to UDEnglish, cuz they dont have the same tagset.} In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

Compared to the coarse-grained \yicomment{fine-grained?}POS tagging effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that used by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} [YICOMMENT: should be OCONNOR's paper? TOKENIZATION?]. In particular, Gimpel et al.~[YICOMMENT: SAME HERE] opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}.  
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check} \yjcomment{checked}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
{\argmin}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} -p(a
	\mid s_i) \cdot \log q(a \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a stack of the state-of-the-art systems (namely, the {\it SOTA stack}):
Stanford CoreNLP tokenizer,
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
Our system differs with the SOTA stack in the tokenization and parser components.
From Table \ref{tbl:pipline}, our system outperforms the SOTA stack when
evaluated in pipeline manner.
The results also emphasize the
importance of segmentation:  without gold segmentation, UD parsing
performance drops by more than four points.
